Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
removed some white space

\begin{proof}
	\textbf{Case 1:} First, consider the case $\bar{b}_2 =0$. As $b_2 \to 0$, we have:
	\begin{equation*}
		B^{b_2} \to 0, \quad B^{\eta,b_2} \to 0,
	\end{equation*}
	and $\lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$, $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$. We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that:
	$$\lim_{b_2 \to 0} PoA = 1.$$

	\textbf{Case 2:} Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have:
	\begin{equation*}
	\begin{array}{l}
		\lambda \longrightarrow 0\\
		\displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0 \\
		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0,
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
	Moreover, we have $\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0 $ and $\lim_{b_2 \to 0}\delta^{-,b_2}_u = 0$, so that $\lim_{b_2 \to 0}(\delta^{+}_u - \delta^{-}_u) = -2 A^u > 0$. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
	$$\lim_{b_2 \to 0}u^{b_2}_t = 0 .$$
	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough. Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 < b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
	\begin{equation*}
	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\qquad \forall  \  t \in [0,T]
	\end{equation*}

@@

	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
	and thus,
	$$ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$$
	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that $$\lim_{b_2 \to 0} PoA^{b_2} = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC^{b_2}}{\displaystyle \lim_{b_2 \to 0} SC^{MKV,b_2} } =: PoA^{b_2 \to 0} > 1.$$

@@

\begin{proof}
	% case when b2 bar \to infty
	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{\bar{b}_2} \to 0,\\
	B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
	\qquad
	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
	and, for all $0 \leq t < T$:
	\begin{equation*}
	\begin{array}{l}
	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
	\end{array}
	\end{equation*}

	Next, we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$. Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$. Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	\begin{equation}
	\left\vert u_t^{\bar{b}_2} \right\vert 
	\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 3 c_{\delta_u^{\bar{b}_2 \to \infty}} + 1
	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
	\end{equation}
	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,upper}$, 
	\begin{equation}
	\sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M.
	\label{eq:ut_wt_uniform_upper_bound_b2_bar_infty}
	\end{equation}
	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$. Denote $\zeta: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$. Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
	\begin{equation}
	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} } 
	\geq  \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
	\label{eq:ut_lower_bound_b2_bar_infty}
	\end{equation}

@@

% proposition b1 and b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming assumption \ref{assumption}, the initial condition satisfies $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{b_1 \to 0} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{\bar{b}_1 \to 0} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	\textbf{Cases 1 and 2:} First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon},
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

@@

	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem,
    \begin{equation*}
        0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty.
    \end{equation*}
    By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus:
    $$0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$$
    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.

@@

	% case 4: b1 bar to infinity
	\textbf{Case 4:} Now, consider $\bar{b}_1 \to \infty$.
	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:
	\begin{equation*}
	\begin{split}
	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u&=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty,\\
	-\delta^{-,\bar{b}_1}_u&=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,\\
	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}&=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} \frac{\sqrt{\left(\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1
	\end{split}
	\end{equation*}
	We also have for $t\in [0,T)$:
	\begin{equation*}
	\begin{split}
	\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
	\xrightarrow[\bar{b}_1 \to \infty]{}0,
	\end{split}
	\end{equation*}
	which implies:
	\begin{equation*}
	\lim_{\bar{b}_1\to \infty}\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0.
	\end{equation*}
	Therefore, for $t \in [0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}.
	\end{equation*}
	By the same arguments, we have for $t \in [0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}.
	\end{equation*}

>>>>

\begin{proof}
	\textbf{Case 1:} First, consider the case $\bar{b}_2 =0$. As $b_2 \to 0$, we have:
	\begin{equation*}
		B^{b_2} \to 0, \quad B^{\eta,b_2} \to 0,
	\end{equation*}
	and $\lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$, $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$. We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that $\lim_{b_2 \to 0} PoA = 1.$

	\textbf{Case 2:} Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have:
	\begin{equation*}
	\begin{array}{l}
		\lambda \longrightarrow 0, \quad \displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0, \quad C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0,
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
	Moreover, we have $\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0 $ and $\lim_{b_2 \to 0}\delta^{-,b_2}_u = 0$, so that $\lim_{b_2 \to 0}(\delta^{+}_u - \delta^{-}_u) = -2 A^u > 0$. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$, $\lim_{b_2 \to 0}u^{b_2}_t = 0.$

	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough. Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 < b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
	\begin{equation*}
	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\qquad \forall  \  t \in [0,T].
	\end{equation*}

@@

	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$
	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that: $$\lim_{b_2 \to 0} PoA^{b_2} =: PoA^{b_2 \to 0} > 1.$$
\end{proof}

@@

\begin{proof}
	% case when b2 bar \to infty
	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{\bar{b}_2} \to 0, \quad B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
	\qquad
	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
	and, for all $0 \leq t < T$:
	\begin{equation*}
	\begin{array}{l}
	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
	\end{array}
	\end{equation*}

	Next, we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$. Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$. Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	\begin{equation}
	\left\vert u_t^{\bar{b}_2} \right\vert 
	\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 3 c_{\delta_u^{\bar{b}_2 \to \infty}} + 1.
	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
	\end{equation}
	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,upper}$, 
	\begin{equation}
	\sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M.
	\label{eq:ut_wt_uniform_upper_bound_b2_bar_infty}
	\end{equation}
	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$. Denote $\zeta: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$. Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
	\begin{equation}
	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} } 
	\geq  \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
	\label{eq:ut_lower_bound_b2_bar_infty}
	\end{equation}

@@

% proposition b1 and b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming assumption \ref{assumption}, the initial condition satisfies $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{b_1 \to 0} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{\bar{b}_1 \to 0} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	\textbf{Cases 1 and 2:} First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon},
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

@@

	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$. By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.

@@

	% case 4: b1 bar to infinity
	\textbf{Case 4:} Now, consider $\bar{b}_1 \to \infty$.
	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:
	\begin{equation*}
	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty, \quad -\delta^{-,\bar{b}_1}_u=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,
	\end{equation*}
	\begin{equation*}
	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} \frac{\sqrt{\left(\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1.
	\end{equation*}
	We also have for $t\in [0,T)$:
	$$\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
	\xrightarrow[\bar{b}_1 \to \infty]{}0,$$
	which implies:
	$
	\lim_{\bar{b}_1\to \infty}\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0.
	$
	Therefore, for $t \in [0,T)$:
	$\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}$. By the same arguments, we have for $t \in [0,T)$: $\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}$.

	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$ and $\lim_{\bar{b}_1 \to \infty}B (D^{w})^2 + 2 A^{w,\bar{b}_1} D^{w} - C^{w}=-\infty$,   from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,lower}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, we have:
	$$\max \left\{ \left|\frac{u^{\bar{b}_1}_0}{\bar{b}_1}-\frac{1}{B} \right|,\left|\frac{w^{\bar{b}_1}_{T/2}}{\bar{b}_1}-\frac{2}{B} \right| \right\} <\frac{1}{4B},$$
	and the functions $t \mapsto u_t^{\bar{b}_1}$ and $ t \mapsto w_t^{\bar{b}_1}$ are decreasing. Thus, for all $t \in [0, T/2]$ we have:
	\begin{equation*}
	    0< \frac{u_t^{\bar{b}_1}}{\bar{b}_1} \leq \frac{u_0^{\bar{b}_1}}{\bar{b}_1} \leq \frac{1}{B} + \frac{1}{4B}  \leq \frac{2}{B} - \frac{1}{4 B} \leq \frac{w_{T/2}^{\bar{b}_1}}{ \bar{b}_1} \leq \frac{w_t^{\bar{b}_1}}{\bar{b}_1}. 
	\end{equation*}
	Thus, for all $\bar{b}_1 \geq \bar{b}_1^{*,lower}$ and all $t \in [0,T/2]$,
	\begin{equation}
	  \left\vert  \frac{w^{\bar{b}_1}_t}{\bar{b}_1}-\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \right\vert \geq \frac{1}{2B}.
	\label{eq:lower_bound_u_w}
	\end{equation}

	Note that $\eta_t$, and therefore $v_t$, are independent of $\bar{b}_1$. Thus,
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}=\frac{1}{2\bar{b}_1^2}\left[\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T\right] + \frac{w^{\bar{b}_1}_0}{2\bar{b}_1^2} (\mathbb{E}(\xi))^2 \xrightarrow[\bar{b}_1 \to \infty]{}0.	
	\end{equation*}
